---
title: "Dry Season Phenotype Data Analysis"
author: "Graeme Vissers"
date: "9/26/21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("./src/DS_pheno_data_vis.R")
```

## Dry Season Phenotype Data Analysis

### Background
Three rice varieites, IR64, IR09L204 (IR108-3), and Nipponbare, were grown in the dry season (sown January 8th, 2021) under four different conditions of nitrogen and water availability (Low N & Low W, Low N & High W, High N & Low W, High N & High W). The following plots demonstrate various phenotypic data gathered from the rice under these varying conditions.

### Leaf Water Potential (LWP)

```{r}
lwp_bars
```

### Porometer

```{r}
porometer_bars
```

### Crownroot Number

```{r}
crownroot_bars
```

### Shoot Dry Weight (SDW)

```{r}
sdw_bars
```

### Tiller Number

```{r}
tiller_bars
```

### Plant Height

```{r}
plantht_bars
```

### Days to Flowering (DTF)
#### Days until 50% of plants have flowered

```{r}
dtf_bars
```

